{\plant}: A package for modelling forest trait ecology \& evolution

### 2015-05-29 ms.tex
More vignette name fixes

% TODO: In favour of dropping this whole paragraph?
It is hoped that the approach here can be used to inform both future
empirical research and model development in neighbouring areas.
{\plant} aims to bridge the gap between detailed physiological models
and large-scale mechanistic models of plant growth \citep{Cramer-2001,
  Sitch-2003, Dekauwe-2014}.  As noted above, most large-scale
mechanistic models of plant growth do not explicitly model size
structure, so remain unable to investigate demographic phenomena }. At
the same time, much attention is paid to detailed leaf-level
physiology. {\plant} aims to bridge this gap that emerged in the model
landscape, where detailed physiology and size-structured dynamics
combine to drive forest structure and function via traits.

@@

\section{Default physiological model for {\plant}}\label{sec:FFW16}

@@

\section{Modelling demography in the {\plant} package}\label{sec:demography}

>>>>

% TODO: In favour of dropping this whole paragraph?
It is hoped that the approach here can be used to inform both future
empirical research and model development in neighbouring areas.
{\plant} aims to bridge the gap between detailed physiological models
and large-scale mechanistic models of plant growth \citep{Cramer-2001,
  Sitch-2003, Dekauwe-2014}.  As noted above, most large-scale
mechanistic models of plant growth do not explicitly model size
structure, so remain unable to investigate demographic phenomena. At
the same time, much attention is paid to detailed leaf-level
physiology. {\plant} aims to bridge this gap that emerged in the model
landscape, where detailed physiology and size-structured dynamics
combine to drive forest structure and function via traits.

@@

\section{Plant physiological model}\label{sec:FFW16}

@@

\section{Modelling demography of plants, patches and metapopulations}\label{sec:demography}
